---
title: "ISE 599 HW 1"
author: "Shaoqian Chen"
date: "1/28/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
#library(readr)
library(MASS)
library(help=MASS)
library(ISLR)
library(lubridate)
library(rlang)
library(dplyr)
library(readr)
data1 = read.csv("crime.csv")
```

```{r}
#data2 is the updated dataset without column "Precinct", "Sector", "Beat"
names(data1)<-c("Report.Number","ODate","OTime","RDate","RTime","category","Description","Precinct","Sector","Beat","Neighborhood")
keep <- c("Report.Number","ODate","OTime","RDate","RTime","category","Description","Neighborhood")
data2 <- data1[keep]
```

```{r}
summary(data2)
```



# Question 1
## Find the number of neighborhoods and crime categories in the dataset

```{r}
#Return the number of neighborhoods
length(table(data2$Neighborhood))

#Return the numnber of crime categories
length(table(data2$category))
```
## 59 Neighborhood; 

## 31 Crime Categories


# Question 2
## Report the total number of crimes in each neighborhood. What neighborhood is most dangerous?
```{r}
library(magrittr)
dataQ2<-data2[c("Report.Number","Neighborhood")]
table(data2$Neighborhood)[table(data2$Neighborhood) %>% which.max]

```
## The most dangerous neighborhood is DOWNTOWN COMMERCIAL, it has 45127 crimes


# Question 3
```{r}
#Question 1 using pipe
library(magrittr)
data2$Neighborhood %>% 
  unique %>%
  length

data2$category %>% 
  unique %>%
  length
```
## Same result as the previous questions.
```{r}
dataQ3<-data2 %>%
  group_by(Neighborhood = tolower(Neighborhood)) %>%
  summarise(count = n())
dataQ3
```
## According to the table above Downtown Commercial(45127 Crimes) is more dangerous than other area



# Question 4
```{r}
QueenAnne <- data2$Neighborhood=="QUEEN ANNE"
dataQ4 <- data2[QueenAnne,]
max(summary(dataQ4$category))
```

```{r}
summary(dataQ4$category)
which.max(table(dataQ4$category))
```
## According to the summary, the most frequent crime category in the Queen Anne neighborhood is "Car Prowl"




# Question 5 
## Report a two-column table comparing the number of crimes per month(from RDate) What month seems to be more dangerous?
```{r}
library(lubridate)
head(data2)
```
```{r}
dataQ5 <- data2[c("RDate")]
month <- c(1,2,3,4,5,6,7,8,9,10,11,12)
dataQ5_1 <- data.frame("Month" = month,"Total_Num"=c(0))
head(dataQ5)
```

```{r}
library(stringr)
a1 = str_split(dataQ5$RDate,"/")
month <- rep(0,length(a1))
```

```{r}
for(i in 1:length(a1))
  {
    month[i] = a1[[i]][1]
}
dataQ5$Month = month
head(dataQ5)
```

```{r}
Q5_ans<-as.data.frame(table(dataQ5$Month))
names(Q5_ans)<-c("Month","Number_Crimes")
Q5_ans
```
## May seems to be more dangerous.




# Question 6 
## Draw a lineplot of the number of crimes as a function of month (in RDate)
```{r}
plot(table(dataQ5$Month),type="o")
```


# Question 7 
## Use vertical barplots to compare the number of crimes by category in Seattle.

```{r}
dataQ7 <- data2$category
as.data.frame(table(dataQ7))
```

```{r}
barplot(table(dataQ7), main="Crime Distribution",
   xlab="Type of Crimes",cex.axis =0.4,cex.names = 0.3,las=2)
```


